---
title: "Lab 1: the tidyverse"
output:
  html_document:
    df_print: paged
---



Firstly, load the library `tidyverse`.
```{r message=FALSE}
library(tidyverse)
```



## The tibbles Chapter
### Create a small tibble manually
```{r}
tibble(x = 1, y = 2, z = runif(10))
```


### Exercise 1
We can use a function called `is_tibble()`.
```{r}
is_tibble(mtcars)
is_tibble(mpg)
```


### Exercise 2
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
tb <- tibble(abc = 1, xyz = "a")
tb$x
tb[, "xyz"]
tb[, c("abc", "xyz")]
```
`data.frame` can let us just use the first few letters instead of the full name of a column with `$` while `tibble` needs the full name. It saves time somtimes but it will also lower legibility and may cause errors easily when there are other columns that have similar names.

Another feature for `data.frame` is that when there is one column is called, it will return a vector not a dataframe. This may cause error when there are downstream processings that only accept dataframe.


### Excersice 4
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
select(annoying, `1`)
ggplot(data = annoying, mapping = aes(x = `1`, y = `2`)) + geom_point()
mutate(annoying, `3` = `2` / `1`)
mutate(annoying, `3` = `2` / `1`) %>% rename(one = `1`, two = `2`, three = `3`)
```


### Exercise 5
From the documentation: enframe() converts named atomic vectors or lists to one- or two-column data frames.


### Exercise 6
We can use `options(tibble.print_max = n, tibble.print_min = m)`.



## The readr Chapter
### Exercise 1
We can use `read_delim(data, delim = "|")`.


### Exercise 2
From the documrntation we can find `col_names`, `col_types`, `locale`, `na`, `quoted_na`, `quote`, `trim_ws`, `n_max`, `guess_max`, `progress`, `skip_empty_rows`.


### Exercise 4
```{r}
read_delim("x,y\n1,'a,b'", delim = ",", quote = "'")
```


### Exercise 5
```{r}
read_csv("a,b\n1,2,3\n4,5,6")
```
There are only two headers but there are three data colunms. `read_csv` truncates the last header.
```{r}
read_csv("a,b,c\n1,2\n1,2,3,4")
```
There are three headers. In the first row, there are two entries instead of three. And in the second row, there are four entries instead of three.`read_csv` uses the `NA` to represent the missing entry and throw the fourth entry of the second row away.
```{r}
read_csv("a,b\n\"1")
```
The first `"` can be parsed as a closing quote of the data, but `read_csv` corrects it. The second entry is missing and `read_csv` uses `NA`.
```{r}
read_csv("a,b\n1,2\na,b")
```
There's nothing wrong.
```{r}
read_csv("a;b\n1;3")
```
`read_csv` is not used to import semicolon seperated data. Use `read_csv2` instead.



## The tidy chapter
### Exercise 3
Because, "cases" and "populations" are two different variables, we need to "spread" the "cases" and "population" into new columns.


### Exercise 2
The years are not quoted with backticks. `tidyr` may regard them as the index of columns not the names.



## The "database-like stuff"" with dplyr chapter
### Exercise 1
```{r}
library(nycflights13)
mutate(flights, flight_key = row_number(flights$day))
```


### Exercise 2
```{r}
library(nycflights13)
airports2 <- select(airports, faa, lat, lon)
flights %>% left_join(airports2, c("origin" = "faa")) %>% rename("ori_lat" = "lat", "ori_lon" = "lon") %>% left_join(airports2, c("dest" = "faa")) %>% rename("dest_lat" = "lat", "dest_lon" = "lon")
```
The airports tibble is modified for better visualization.